---
title: 'Final Project'
author: 'Siji Akinkugbe, Gad Runkundo & Craig Chipendo'
output:
  pdf_document: default
  word_document: default
always_allow_html: yes
fontsize: 11pt
---
```{r}
library(dplyr)
library(glmnet)
library(tensorflow)
library(keras3)
library(Matrix)
library(readr)
library(lubridate)
library(tidyr)

```



### Importing Walmart Dataset
```{r}
stores <- read.csv('https://zhang-datasets.s3.us-east-2.amazonaws.com/stores.csv')
sales <- read.csv('https://zhang-datasets.s3.us-east-2.amazonaws.com/sales.csv')
features <- read.csv('https://zhang-datasets.s3.us-east-2.amazonaws.com/features.csv')
```

### Combining datasets to create one dataset

```{r}

sales <- sales %>%
  mutate(Date = parse_date_time(Date, orders = c("ymd", "mdy", "dmy")))

features <- features %>%
  mutate(Date = parse_date_time(Date, orders = c("ymd", "mdy", "dmy"))) %>%
  select(-IsHoliday)


final_dataset <- sales %>%
  left_join(features, by = c("Store", "Date")) %>%
  left_join(stores, by = "Store")


final_dataset <- final_dataset %>%
  mutate(
    Date = as.Date(Date), 
    across(starts_with("MarkDown"), ~replace_na(., 0)),
    across(CPI, ~replace_na(., median(., na.rm = TRUE))),
    across(Unemployment, ~replace_na(., median(., na.rm = TRUE)))
  ) 
  
final_dataset<- final_dataset[final_dataset$Weekly_Sales >= 0, ]
rownames(final_dataset) <- NULL


  

str(final_dataset$Date)
head(final_dataset)
summary(final_dataset)

nrow(final_dataset)
sum(is.na(final_dataset))

```
```{r}
final_dataset <- final_dataset %>%
  mutate(
    Week  = isoweek(Date),   # week of year
    Month = month(Date),     # month
    Year  = year(Date)       # year
  )

markdown_cols <- c("MarkDown1", "MarkDown2", "MarkDown3", "MarkDown4", "MarkDown5")
final_dataset$TotalMarkDown <- rowSums(final_dataset[, markdown_cols], na.rm = TRUE)
```

## Task 1: Inference: 
To help identify factors that significantly impact sales;
```{r}
lm_model <- lm(Weekly_Sales ~ . - Store -Dept -Date-TotalMarkDown, data=final_dataset)
summary(lm_model)
```
## (T2) Prediction 
To build a predictive model for weekly store sales with high prediction
accuracy. For this task, please use the last 30 weeks as testing data and use the MSE for
prediction error evaluation. Please also evaluate the performance of a deep learning model.

### Train/ Test Split 

```{r}


features <-  c('Store', 'Dept','IsHoliday','Temperature', 'Fuel_Price', 'CPI','Unemployment','Size', 'Type','Week', 'Month', 'Year',              'TotalMarkDown') + markdown_cols  
target <- 'Weekly_Sales'

```




